Geometric Signs on Paleolithic Mobile Objects as Cultural Group Markers

### 2025-01-22 endofquarterpaper.qmd
eco edits

date_graph <- ggplot(signbase_years_cal) +
  aes(x = MedianBP) +
  geom_bar(width = 150) +
  labs(x = "Median calibrated BP")
signbase_3000 <- signbase_years_cal
signbase_3000$site_name <- signbase_years$site_name
signbase_3000 <- signbase_3000 %>% 
  filter(MedianBP < 30000)

>>>>

date_graph <- ggplot(signbase_years_cal) +
  aes(x = MedianBP) +
  geom_bar(width = 150) +
  labs(x = "Median calibrated BP")
